Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
Threats to validity

%-------------------------------
\subsection{Threats to validity}
%-------------------------------

>>>>

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.

Our algorithm to select suitable FWL word widths to model plant behaviour employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.

The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
